\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{datetime}
\usepackage{hyperref}
\newdate{date}{27}{03}{2014}
\date{\displaydate{date}}
\usepackage{filecontents}

\begin{filecontents}{cite.bib}
@book{Craig,
 author = {Craig, John J.},
 title = {Introduction to Robotics: Mechanics and Control},
 year = {1989},
 isbn = {0201095289},
 edition = {2nd},
 publisher = {Addison-Wesley Longman Publishing Co., Inc.},
 address = {Boston, MA, USA},
} 
\end{filecontents}
%opening
\title{Robot Manipulation - Assignment 01}
\author{Prof. Dr. E. Pra{\ss}ler \\Praveen Ramanujam}
\begin{document}
\maketitle


\section{Lab Class}
\begin{itemize}
 \item Introduction to ROS.
 \item Concept of URDF (Universal Description Format).
 \item Launching Robot and Related Topics.
 \item Introduction to TF.
\end{itemize}



\section{Mind Map}3 Points
\begin{itemize}
 \item Provide a mind-map for the Chapter `` Spatial descriptions and transformations
 '' of \cite{Craig}.
 \item For participants who have not been introduced to Frames, the video lecture from Prof. Khatib is recommended
 \footnote{Video Lectures can be found in the LEA Resources Section}.
 \item The e-book is available in the Resources Section of LEA.
\end{itemize}

\section{Exercise} 10 points
\begin{itemize}
\item Solve Matlab Exercise 2a (a,b,c,d) from Chapter 2 of the book \cite{Craig}.
\end{itemize}

\section{ROS -1 } 5 Points
\begin{itemize}
 \item Review through the concepts of ROS (nothing to be submitted for this item) \footnote{Original Paper of ROS can be found in the resources section.} . 
 \item Compare the values listed down in youbot-store \footnote{\url{http://www.youbot-store.com/youbot-developers/software/simulation/kuka-youbot-kinematics-dynamics-and-3d-model}}
and compare how is it related to URDF. Relate in terms of a table.
\end{itemize}

\section{ROS -2 } 2 Points
\begin{itemize}
 \item Rotation Matrices were introduced in the lecture. How many angle-set convention exists ?
 \item Name some other ways of representing orientation in 3-D ?
 \end{itemize}


\bibliographystyle{abbrv}
\bibliography{cite}



\end{document}
